---
title: "potaplan"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{potaplan}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(potaplan)
library(leaflet)
library(dplyr)
```


# Finding Parks within a Distance of Point
To find Parks within 100 km of your coordinates:

```{r}

myparks <- ParksRad("EM83aw")
myparks$parks_filtered

```

To make a map (using leaflet):
```{r}
leaflet(width = 700) %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addCircleMarkers(
    data = myparks$parks_filtered,
    color = "blue",
    radius = 5,
    popup = ~ properties.name
  ) %>%
  addPolygons(
    data = myparks$circleDist,
    color = "red",
    weight = 2,
    fill = FALSE
  )

```




To export to Google Earth, mymaps.google.com, or other GIS you can write as KML:

```{r}
library(sf)
myparks$parks_filtered |>
  transmute(name =properties.name,  description = properties.name, distance_km) |>
  st_write("~/potaparks.kml", delete_layer = T)

```

# Find Parks Along a Path

You can export a route as a KML file, you can upload it and use the potaplan to identify parks within a distance of your route. The potaplan package comes with predefined route as a kml, but you can use `st_read` to read any kml file with 2 points and a path. 

```{r, message=F, warning = FALSE}
myroute <- sf::st_read(system.file("extdata", "directions.kml", package = "potaplan"))
myroute

trip_parks <- ParksPath(myroute)
trip_parks$parks_filtered
```

To make a map (using leaflet):
```{r}

leaflet(width = 700) %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addPolygons(
    data = trip_parks$buffer,
    color = "red",
    weight = 2,
    fill = FALSE
  ) %>%
  addCircleMarkers(
    data = trip_parks$parks_filtered,
    color = "blue",
    radius = 5,
    popup = ~ properties.name
  )
```

